%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
    {Poster Presentations \& Talks (first author)} % Job title
    {} % Organization
    {} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Robinson, H.L., Liu, C., Oliva, A., Fernandez-Ruiz, A. (2022, November). Hippocampo-cortical circuits for selective memory encoding, routing, and replay. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Clark, B.J. (2020,October). Hippocampal replay alterations following moderate prenatal alcohol. Traditional talk at Neuromatch Conference 3.0. \href{https://www.youtube.com/watch?v=YlsuJasxjjg&t=5s&ab_channel=NeuromatchConference}{Talk Link}}    
      \end{cvitems}
    }
\end{cventries}
    
\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Savage, D.D., Hamilton, D.A., Clark, B.J. (2019, October). Hippocampal CA1, CA3, and dentate gyrus place cell firing characteristics in a rat model of moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. Chicago, IL.} 
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Clark, B.J. (2019, October). Disruption of the anterior thalamic head direction cell network impairs the hippocampal place signal. Poster presented at the Society for Neuroscience Conference. Chicago, IL.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, November). Spatial and temporal stability in CA1 hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, September). Spatial and temporal deficits in hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at FASD Awareness Day. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, October). Altered spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the New Mexico EEG and Behavior conference. Albuquerque, NM}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, April). Altered spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the International Conference on Learning and Memory. Huntington Beach, CA.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, March). Reduced Spatial Coding of Hippocampal Place Cells Following Moderate Prenatal Alcohol Exposure. Poster presented at the Gordon Research Conference. Galveston, TX}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Goss, J., Rigg, T., Berkowitz, L. E., Wagner, J. L., Savage, D. D., Hamilton, D. A., \& Clark, B.J. (2017, November). Reduced spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. Washington DC.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J. (2017). Reduced spatial and directional coding by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at the 40th Annual Research Society on Alcoholism Meeting, Denver, CO.}
        \item {\textbf{Harvey, R.E.} (2017). First Characterization of Hippocampal Place Cell firing in a Moderate Prenatal Alcohol Rat Model. Talk delivered at UNM Psychology Research Day, Data Blitz. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Rysanek, J.S., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J., (2017). Reduced directional coding and phase locking by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at UNM Neuroscience day, Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Rysanek, J.S., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J., (2017). Reduced directional coding and phase locking by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at UNM Alcohol Research Poster Session, Albuquerque, NM.}      
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Sneddon, E.A., Yoder, R.M., Clark, B. (2016). Influence of Anterior Thalamic Inactivation on the Retrieval of Spatial Inactivation of the Anterodorsal Thalamic Nuclei Leads to Reference Memory and Working Memory in the Radial Arm Maze. Poster presented at The Annual Society for Neuroscience conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Yoder, R.M., Clark, B. (2016). Inactivation of the anterodorsal thalamus leads to navigational deficits in the radial arm maze. Poster presented at UNM psychology department’s Psychology Research Day. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Yoder, R.M., Clark, B. (2016). Inactivation of the anterodorsal thalamic nuclei leads to navigational deficits in the radial arm maze. Poster presented at the Brain \& Behavioral Health Institute’s Neuroscience day. Albuquerque, NM.}
      \end{cvitems}
    }
\end{cventries}


\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Horton, A. H., Serna, C. E., Terry, C. A.(2015). Video game experience: Perception of self motion and motion sickness in the virtual world. 18th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2015.}
      \end{cvitems}
    }
\end{cventries}


\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2014). Previous training improves egocentric navigation performance in otoconia-deficient mice. Poster presented at the Midwestern Psychological Association, Chicago, IL.}
        \item {\textbf{Harvey, R.E.} (2014). Pretraining improves egocentric navigation performance in otoconia-deficient mice.17th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2014.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2013). Finding Their Way in Space: An Alternative Strategy Improves Navigation Performance in Otoconia-Deficient Mice. Poster presented at the 29th American Society for Gravitational and Space Research, Orlando, FL.}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2013). The head direction signal contributes to accurate navigation in darkness. Program No. 16. 16th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2013.}
      \end{cvitems}
    }
\end{cventries}