%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\cventry
    {Poster Presentations \& Talks} % Job title
    {} % Organization
    {} % Location
    {2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Liu, C., Zhao, Z., Carbajal-Leon, E., Oliva, A., Fernandez-Ruiz, A. (2024, October). Hippocampal-cortical memory consolidation occurs at learning timescales. Chicago, IL.}
        \item {Karaba, L., Robinson, H.L., \textbf{Harvey, R.E.}, Fernandez-Ruiz, A., Oliva, A. (2024, October). A hippocampal circuit mechanism to balance memory reactivation during consolidation. Chicago, IL.}
        \item {Paudel, P., Vogt, C., Liu, C., Zhao, Z., \textbf{Harvey, R.E.}, Niraula, R., Sheehan, M., Fernandez-Ruiz, A., Oliva, A. (2024, October). Social experiences in rewilded mice living in outdoor enclosures reactivate during sleep. Chicago, IL.}
        \item {Berkowitz, L., Rodorova, R., \textbf{Harvey, R.E.}, Cabus, D., Letendre, J., Shimizu, J., Dong, X., Tehrani, N., Jia, J., Roth, S., Fernandez-Ruiz, A., Nishimura, N., Schaffer, C. (2024, October). Mechanisms of context encoding in APP/PS1 mice are rescued by increasing cerebral blood flow by eliminating capillary stalls. Chicago, IL.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Robinson, H.L., Liu, C., Oliva, A., Fernandez-Ruiz, A. (2022, November). Hippocampo-cortical circuits for selective memory encoding, routing, and replay. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Clark, B.J. (2020,October). Hippocampal replay alterations following moderate prenatal alcohol. Traditional talk at Neuromatch Conference 3.0. \href{https://www.youtube.com/watch?v=YlsuJasxjjg&t=5s&ab_channel=NeuromatchConference}{Talk Link}}
        \item {Berkowitz, L.E., \textbf{Harvey, R.E.}, Gabaldon-Parish, M., Roy, V.J., Clark, B.J. (2020,October). Investigation of postsubicular head direction cells in the TgF344-AD rat model of Alzheimer’s disease. Traditional talk at Neuromatch Conference 3.0.}
        \item {James, K.E., Berkowitz, L.E., \textbf{Harvey, R.E.}, Thompson, S.M., Olguin, C.R., Drake, E.N., Pentkowski, N.S., Clark, B.J. (2020,October). The contribution of anxiety to spatial memory deficits in the TgF344-AD rat model of Alzheimer’s disease. Neuromatch Conference 3.0.}
        \item {Berkowitz, L.E., \textbf{Harvey, R.E.}, Clark, B.J. (2020, July). Head direction cells in the TgF344-AD rat model of Alzheimer's disease. Alzheimer's Association International Conference.}      
      \end{cvitems}
    }
\end{cventries}
    
\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Savage, D.D., Hamilton, D.A., Clark, B.J. (2019, October). Hippocampal CA1, CA3, and dentate gyrus place cell firing characteristics in a rat model of moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. Chicago, IL.} 
        \item {Gon\c{c}alves-Garcia, M., Berkowitz, L.E., Donaldson, T., \textbf{Harvey, R.E.}, Wagner, J., Davies, S., Savage, D.D., Clark, B.J. (2019, October). The effects of moderate prenatal alcohol exposure on the organization of exploratory behavior by adult rats. Poster presented at the Society for Neuroscience Conference. Chicago, IL.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L.E., Clark, B.J. (2019, October). Disruption of the anterior thalamic head direction cell network impairs the hippocampal place signal. Poster presented at the Society for Neuroscience Conference. Chicago, IL.}
        \item {Berkowitz, L.E., \textbf{Harvey, R.E.}, Gabaldon-Parish, M., Roy, V. (2019, October). Characterization of cortical and thalamic head direction cells in the TgF344-AD rat model of Alzheimer’s disease. Poster presented at the Society for Neuroscience Conference. Chicago, IL.}
        \item {Berkowitz, L.E., Gabaldon-Parish, M., \textbf{Harvey, R.E.}, Sneddon, E., Clark, B.J. (2019, October). Distributive home base behavior in the TgF344-AD rat model of Alzheimer’s disease. Poster presented at the Society for Neuroscience Conference. Chicago, IL.}
        \item {Gabaldon-Parish, M., Berkowitz, L.E., \textbf{Harvey, R.E.}, Sneddon, E., Clark, B.J. (2019, March). Distributed home base behavior in TgF344-AD rat model of Alzheimer’s disease. Poster presented at UNM Neuroscience day, Albuquerque, NM.}
        \item {Gon\c{c}alves-Garcia, M., Donaldson, T., Berkowitz, L.E., \textbf{Harvey, R.E.}, Gabaldon-Parish, M., Sanchez, L., Goss, J.K., Wagner, J., Davies, S., Tofighi, D., Savage, D.D., Clark, B.J. (2019, March). The effects of moderate prenatal alcohol exposure on the organization of exploratory behavior by adult female rats. Poster presented at UNM Neuroscience day, Albuquerque, NM.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {Sanchez, L.M., \textbf{Harvey, R.E.}, Benthem, D., Goss, J., Johnson, S.A., Turner, S.M., Savage. D.D., Burke, S.N., \& Clark, B.J., (2018, November). The effect of moderate prenatal alcohol exposure on object discrimination by adult rats. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
        \item {Yoder, R.M., \textbf{Harvey, R.E.}, Rutan, S.A., Carstensen, L.C., Willey, G.R., Terry, C.A., Siegel, J.J., \& Clark, B.J., (2018, November). Linear self-motion cues contribute to hippocampal place cells: Functional implications. Current Biology, 28(11), 1803-1810. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, November). Spatial and temporal stability in CA1 hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, September). Spatial and temporal deficits in hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at FASD Awareness Day. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, October). Altered spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the New Mexico EEG and Behavior conference. Albuquerque, NM}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, April). Altered spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the International Conference on Learning and Memory. Huntington Beach, CA.}
        \item {Berkowitz, L. E., \textbf{Harvey, R.E.}, \& Clark, B. J. (2018, April). Characterization of Head Direction Cells in the TgF344-AD Rat Model of Alzheimer’s Disease. Poster presented at the International Conference on Learning and Memory. Huntington Beach, CA.}
        \item {\textbf{Harvey, R.E.}, Berkowitz, L. E., Savage, D. D., Hamilton, D. A., \& Clark, B. J. (2018, March). Reduced Spatial Coding of Hippocampal Place Cells Following Moderate Prenatal Alcohol Exposure. Poster presented at the Gordon Research Conference. Galveston, TX}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {Berkowitz, L. E. Thompson, S. M., Drake, E. N., Madden, J. T., Sneddon, E. A., \textbf{Harvey, R.E.}, Clark B. J. (2017, November). Sex specific spatial navigation and spatial memory impairment in the TgF344-ad rat model of Alzheimer’s disease. Poster presented at the Society for Neuroscience Conference. Washington DC.}
        \item {\textbf{Harvey, R.E.}, Goss, J., Rigg, T., Berkowitz, L. E., Wagner, J. L., Savage, D. D., Hamilton, D. A., \& Clark, B.J. (2017, November). Reduced spatial coding of hippocampal place cells following moderate prenatal alcohol exposure. Poster presented at the Society for Neuroscience Conference. Washington DC.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J. (2017). Reduced spatial and directional coding by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at the 40th Annual Research Society on Alcoholism Meeting, Denver, CO.}
        \item {\textbf{Harvey, R.E.} (2017). First Characterization of Hippocampal Place Cell firing in a Moderate Prenatal Alcohol Rat Model. Talk delivered at UNM Psychology Research Day, Data Blitz. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Rysanek, J.S., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J., (2017). Reduced directional coding and phase locking by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at UNM Neuroscience day, Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Rigg, T., Goss, J., Rysanek, J.S., Wagner, J.L., Savage, D.D., Hamilton, D.A., Clark, B.J., (2017). Reduced directional coding and phase locking by hippocampal place cells following moderate prenatal alcohol exposure in the rat. Poster presented at UNM Alcohol Research Poster Session, Albuquerque, NM.}      
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {Thompson, S.M., \textbf{Harvey, R.E.}, Sanchez, L.M., Winter, S.S., Clark, B.J. (2016). Directional Discrimination in an Object-Place Paired Associate Memory is Impaired after Muscimol Inactivation of the Anterior Thalamus. Poster presented at The Annual Society for Neuroscience conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Sneddon, E.A., Yoder, R.M., Clark, B. (2016). Influence of Anterior Thalamic Inactivation on the Retrieval of Spatial Inactivation of the Anterodorsal Thalamic Nuclei Leads to Reference Memory and Working Memory in the Radial Arm Maze. Poster presented at The Annual Society for Neuroscience conference. San Diego, CA.}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Yoder, R.M., Clark, B. (2016). Inactivation of the anterodorsal thalamus leads to navigational deficits in the radial arm maze. Poster presented at UNM psychology department’s Psychology Research Day. Albuquerque, NM.}
        \item {\textbf{Harvey, R.E.}, Thompson, S., Sanchez, L.M., Yoder, R.M., Clark, B. (2016). Inactivation of the anterodorsal thalamic nuclei leads to navigational deficits in the radial arm maze. Poster presented at the Brain \& Behavioral Health Institute’s Neuroscience day. Albuquerque, NM.}
      \end{cvitems}
    }
\end{cventries}


\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {Lawton C. A., \textbf{Harvey, R.E.}, Horton, A. H., Terry, C. A., Serna, C. E. (2015). Effects of video game experience on perceived self-motion in a stereoscopic display. Poster presented at the Association for Psychological Science. New York, NY.}
        \item {Lawton C. A., \textbf{Harvey, R.E.}, Horton, A. H., Terry, C. A., Serna, C. E. (2015). Sex Differences in Perceived Self-Movement in a Stereoscopic Head-Mounted Display. Poster presented at the Midwestern Psychological Association, Chicago, IL.}
        \item {\textbf{Harvey, R.E.}, Horton, A. H., Serna, C. E., Terry, C. A.(2015). Video game experience: Perception of self motion and motion sickness in the virtual world. 18th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2015.}
      \end{cvitems}
    }
\end{cventries}


\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2014). Previous training improves egocentric navigation performance in otoconia-deficient mice. Poster presented at the Midwestern Psychological Association, Chicago, IL.}
        \item {Lawton, C. A., Brockman, S. N., Goebel, E. A., Long, A. M., Phillips, E. L., \textbf{Harvey, R.E.}, Kirby, S. L., \& Rosbrugh, H. H. (2014). Sex, handedness, and virtual navigation. Poster presented at the Midwestern Psychological Association, Chicago, IL.}
        \item {\textbf{Harvey, R.E.} (2014). Pretraining improves egocentric navigation performance in otoconia-deficient mice.17th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2014.}
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.35em}
        \item {Kirby, S. L., \textbf{Harvey, R.E.}, Goebel, E. A., Köppen, J. R., Wallace, D. G., \& Yoder, R. M. (2013) Head direction signal degradation impairs spatial learning. Poster presented at Society for Neuroscience, San Diego, CA.}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2013). Finding Their Way in Space: An Alternative Strategy Improves Navigation Performance in Otoconia-Deficient Mice. Poster presented at the 29th American Society for Gravitational and Space Research, Orlando, FL.}
        \item {Kirby, S. L., \textbf{Harvey, R.E.}, \& Yoder, R. M. (2013). Head direction signal degradation contributes to navigation impairments. Poster presented at the Midwestern Psychological Association, Chicago, IL.}
        \item {\textbf{Harvey, R.E.} \& Yoder, R. M. (2013). The head direction signal contributes to accurate navigation in darkness. Program No. 16. 16th Annual Student Research And Creative Endeavor Symposium. Purdue University Fort Wayne, 2013.}
      \end{cvitems}
    }
\end{cventries}