
\cvsection{Publications}
\begin{cventries}

%---------------------------------------------------------
% \cventry
%     {Preprints} % Job title
%     {} % Organization
%     {} % Location
%     {} % Date(s)
%     {
%       \begin{cvitems} % Description(s) bullet points
%       \setlength\itemsep{0.5em}
%         \item {\href{https://doi.org/10.1101/2023.02.15.528683}{Soula, M., Maslarova, A., \textbf{Harvey, R.E.}, Valero, M., Brandner, S., Hamer, H., Fernandez-Ruiz, A, Buzsaki, G. (2023). Intricate epileptiform discharges affect memory in an Alzheimer's Disease mouse model. bioRxiv.}}
%         \item {\href{https://doi.org/10.1101/2021.06.29.450435}{\textbf{Harvey, R.E.} Berkowitz, L.E., Savage, D.D., Clark, B.J. (2021). Prenatal alcohol exposure disrupts hippocampal sharp-wave ripple-associated spike dynamics. bioRxiv.}}
%       \end{cvitems}
%     }
    
\cventry
    {} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.5em}
            \item {\href{https://doi.org/10.1016/j.neuron.2023.04.015}{\textbf{Harvey, R.E.} Robinson, H.L., Liu, C., Oliva, O., Fernandez-Ruiz, A. (2023). Hippocampo-cortical circuits for selective memory encoding, routing, and replay. Neuron.}}
            \item {\href{https://doi.org/10.1073/pnas.2302676120 }{Soula, M., Maslarova, A., \textbf{Harvey, R.E.}, Valero, M., Brandner, S., Hamer, H., Fernandez-Ruiz, A, Buzsaki, G. (2023). Intricate epileptiform discharges affect memory in an Alzheimer's Disease mouse model. PNAS.}}
            \item {\href{https://doi.org/10.1101/2021.06.29.450435}{\textbf{Harvey, R.E.} Berkowitz, L.E., Savage, D.D., Clark, B.J. (2021). Prenatal alcohol exposure disrupts hippocampal sharp-wave ripple-associated spike dynamics. bioRxiv.}}
            \item {\href{https://doi.org/10.1016/j.cub.2020.06.077}{\textbf{Harvey, R.E.}, Berkowitz, L.E., Savage, D.D., Hamilton, D.A., Clark, B.J. (2020). Altered hippocampal place cell representation and theta rhythmicity following moderate prenatal alcohol exposure. Current Biology.}\href{https://doi.org/10.1016/j.cub.2020.07.020}{{ (\scriptsize Commentary: Wirt, R.A., McNeela, A.M., \& Hyman, J.M. (2020). Current Biology})}}
            \item {\href{https://doi.org/10.1016/j.neubiorev.2019.09.018}{\textbf{Harvey, R.E.}, Berkowitz, L. E., Hamilton, D. A., \& Clark, B. J. (2019). The Effects of Developmental Alcohol Exposure on the Neurobiology of Spatial Processing. Neuroscience \& Biobehavioral Reviews.}}
            \item {\href{https://doi.org/10.3389/fncir.2019.00075}{Xu, Z., Wu, W., Winter, S. S., Mehlman, M. L., Butler, W. N., Simmons, C. M., \textbf{Harvey, R.E.}, Berkowitz, L.E., Chen, Y., Taube, J.S., Wilber, A. A., \& Clark, B.J. (2019). A Comparison of Neural Decoding Methods and Population Coding Across Thalamo-Cortical Head Direction Cells. Frontiers in Neural Circuits.}}
            \item {\href{https://doi.org/10.1038/s41598-018-34368-w}{Berkowitz, L. E., \textbf{Harvey, R.E.}, Drake, E., Thompson, S. M., \& Clark, B. J. (2018). Progressive impairment of directional and spatially precise trajectories by TgF344-Alzheimer’s disease rats in the Morris Water Task. Scientific reports.}} 
            \item {\href{https://doi.org/10.1016/j.cub.2018.04.034}{\textbf{Harvey, R.E.}, Rutan, S. A., Willey, G. R., Siegel, J. J., Clark, B. J., \& Yoder, R. M. (2018). Linear self-motion cues support the spatial distribution and stability of hippocampal place cells. Current Biology.}}
            \item {\href{https://doi.org/10.3389/fnins.2017.00094}{\textbf{Harvey, R.E.}, Thompson, S. M., Sanchez, L. M., Yoder, R. M., \& Clark, B. J. (2017). Post-training inactivation of the anterior thalamic nuclei impairs spatial performance on the radial arm maze. Frontiers in neuroscience.}} 
            \item {\href{https://doi.org/10.1016/j.nlm.2016.06.002}{Clark, B. J., \& \textbf{Harvey, R.E.} (2016). Do the anterior and lateral thalamic nuclei make distinct contributions to spatial representation and memory? Neurobiology of learning and memory.}}
      \end{cvitems}
    }
    
\cventry
    {Book Chapters} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \setlength\itemsep{0.5em}
          \item {\href{https://doi.org/10.1016/B978-0-12-815868-5.00043-8}{Berkowitz, L.E., \textbf{Harvey, R.E.}, Clark B.J. (2020). Spatial Navigation and Alzheimer’s disease. In: C. Martin\& V.R. Preedy (Eds.), The Neuroscience of Dementia: Genetics, Neurology, Behavior, and Diet in Dementia (1st ed., Vol. 2, pp. 677-692). Academic Press.}}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}